---
title: "Homework IV, due June 3rd"
author: "M Loecher"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
data(Smarket)
```

**This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.**

## 1. Review your understanding of **logistic regression**
   * Read chapters 4.1, 4.2, 4.3.1-4.3.4 
   * Reproduce Lab Exercises 4.6.1 and 4.6.2 

### Lab session 4.6.1 

```{r, collapse = TRUE}
names(Smarket)
dim(Smarket)
summary(Smarket)
```
```{r}
cor(Smarket[,-9])
```
```{r}
attach(Smarket)
plot(Volume)
```

### Lab session 4.6.2
```{r}
glm.fit = glm(Direction ~ Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Smarket, family =binomial)
summary(glm.fit)
```

```{r, collapse = TRUE}
# Accessing just the coefficients
coef(glm.fit)
# Accessing particular values in Summary
summary(glm.fit)$coef
## Access p Values only
summary(glm.fit )$coef [,4]
```

```{r, collapse = TRUE}
glm.probs = predict(
  glm.fit,
  type = "response" #Output it in P(Y=1|X)
  )
# Show first 10 probabilities
glm.probs[1:10] 
# prove that the predict correspond to the probs of the market going up (Y = Up = 1)
contrasts (Direction)
```

```{r}
# Make prediction on going down
## Create a vector w 1250 elements with "Down"
glm.pred = rep("Down",1250)
## Change to "Up" when pred value is >0.5
glm.pred[glm.probs >.5] = "Up"

# output result as table matrix to determine evaluate prediction
table(glm.pred, Direction)
## mean to output the fraction of correctly predicted days 
mean(glm.pred == Direction)
```

```{r, collapse = TRUE}
# optimise training error rate
train = (Year<2005)
## Create subset for 2005
Smarket.2005 = Smarket [! train ,]
dim(Smarket.2005)

## create vector w directions in 2005
Direction.2005= Direction [! train]

# Create Model using subset data
glm.fit=glm(Direction ~ Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Smarket, family=binomial, subset=train)
## Obtain Probabilities
glm.probs =predict (glm.fit, Smarket.2005, type="response" )

# Compute predictions for 2005 
glm.pred=rep ("Down" ,252)
glm.pred[glm.probs > .5]= "Up"

# Evaluate predictions
table(glm.pred ,Direction.2005)
## Correct Predictions
mean(glm.pred == Direction.2005)
## Incorrect Predictions 
mean(glm.pred != Direction.2005)
```
```{r, collapse=TRUE}
# refit the model using only Lag1 and Lag2
glm.fit=glm(Direction ~ Lag1+Lag2, data=Smarket, family=binomial, subset=train)
glm.probs =predict (glm.fit, Smarket.2005, type="response" )
glm.pred=rep ("Down" ,252)
glm.pred[glm.probs > .5]= "Up"
table(glm.pred ,Direction.2005)
## Correct Predictions
mean(glm.pred == Direction.2005)
## Accuracy on predicting Up
106/(106+76)
```
Suppose that we want to predict the returns associated with particular values of `Lag1` and `Lag2`. In particular, we want to predict Direction on a day when `Lag1` and `Lag2` equal 1.2 and 1.1, respectively, and on a day when they equal 1.5 and −0.8. We do this using the `predict()` function.
```{r}
predict(glm.fit, newdata = data.frame(Lag1=c(1.2 ,1.5), Lag2=c(1.1 , -0.8) ), type ="response" )
```

### 2. Load the Wage data from the ISLR library and define a new column
```{r}
data(Wage)
Wage$Information__job = Wage$jobclass == "2. Information"
```
#### Fit a logistic regression modeling `Information__job` as a function of education.
```{r}
attach(Wage)
Wage.fit = glm(Information__job~education, family = binomial)
summary(Wage.fit)
contrasts(Information__job)
```
#### Compared to the baseline: by what (multiplicative) factor are the odds of a HS Grad defaulting higher or lower of being in the Information category of jobs ?

Compared to the baseline, the odds of a HS Grad to get a job in the information category are *increased* by a factor of `r exp(0.2492)`

#### What is the probability of a person with an advanced degree of being in the Information category of jobs ?
```{r}
# Manual Calculation
Odds = exp(coef((Wage.fit))[1]+coef(Wage.fit)[5])
##Probability 
unname(Odds/(1+Odds))

# Using Predict
predict(Wage.fit, newdata = data.frame(education = factor("5. Advanced Degree") ), type ="response" )
```

