---
title: "Homework VI, due June 17th"
author:
- M Loecher
- Yilun Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.

1. Learn about **Cross Validation** using the book [An Introduction to Statistical Learning](https://westminster.instructure.com/courses/2915670/files/172215801) (formerly at http://faculty.marshall.usc.edu/gareth-james/ISL/)
   * Read chapter 5.1

2. Write your own cross validation code ! The function should take as input the formula and data used to fit the model, the number of folds ($k$) and return the vector of $k$ losses (i.e. either RSS or deviance):

##### My Function
```{r}
my.cv.glm = function(formula, data, k, family = gaussian){

  #get response column name 
  response = as.character(
    terms(
      as.formula(formula), # Handle formula input as string
      data = data # Handle formula with .
      )[[2]]
  )
  
  #init Output
  cv.err = rep(0,k)
  names(cv.err)=1:k
  
  # Create an vector of index with k equally sized folds 
  folds = cut(1:nrow(data),breaks = k,labels = FALSE)
  
  # randomize dataset
  set.seed(123)
  data=data[sample(nrow(data)),]
  
  #Perform k fold cross validation 
  for(i in 1:k){
    #assign train Data 
    trainIndexes = which(folds!=i,arr.ind=FALSE)
    trainData = data[trainIndexes, ]
    
    #Use trainData to fit the model 
    fit.glm = glm(formula = formula, data = trainData,  family = family)
    
    #calculate MSE and save result
    cv.err[i] = mean(
      (data[,response]-predict(fit.glm, newdata = data))[-trainIndexes]^2, na.rm = TRUE
    )
  }
  return(cv.err)
}

```

###### Function Testing
```{r}
#using titanic data 
library(titanic)
data("titanic_train")
#formula of class formula 
my.cv.glm(Survived ~ Pclass+Sex+Age, data = titanic_train,k=5)
#formula as string
my.cv.glm("Survived ~ Pclass+Sex+Age", data = titanic_train,k=5)
```

```{r}
# generating random data
set.seed(12345)
n = 1000
x = rnorm(n) 
y = ifelse(pnorm(1 + 0.5 * x + rnorm(n)) > 0.5, 1, 0)
my.data = data.frame(y, x)
## testing .
my.cv.glm(y~.,data=my.data,k = 10)
```




