---
title: "Homework VII a, due June 24th"
author: 
- M Loecher
- Yilun Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
```

#### This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.

1. Learn about **L1/L2 Regression** and the elastic net using the book [An Introduction to Statistical Learning](https://westminster.instructure.com/courses/2915670/files/172215801) (formerly at http://faculty.marshall.usc.edu/gareth-james/ISL/)
   * Read chapter 6.2

2. Read the heart data set (https://web.stanford.edu/~hastie/ElemStatLearn//datasets/SAheart.info.txt) into R.
   * Add 10 random columns
   * Find the optimum value for $\alpha$ which results in the minimum cross validated deviance for the regularized logistic regression `chd ~ ., data=heart` 

```{r, eval = TRUE}
heart = read.table("http://www-stat.stanford.edu/~tibs/ElemStatLearn/datasets/SAheart.data", sep=",", head=T,row.names=1)
# Add 10 random columns
set.seed(123)
heart = cbind(heart,matrix(rnorm(nrow(heart)*10),ncol = 10))

#Init params for glmnet
x = model.matrix(chd~.,heart)[,-1]
y = heart$chd
```


```{r}
alpha.grid = seq(0,1,by = 0.05)
foldid=sample(1:10,size=length(y),replace = TRUE)
output = cbind(alpha.grid,0,0)
colnames(output)=c("alpha","lambda","measure")
for (i in 1:nrow(output)){
  my.cv = cv.glmnet(x,y, alpha = alpha.grid[i], foldid = foldid)
  output[i,2]=my.cv$lambda.min
  output[i,3]=min(my.cv$cvm)
}
bestRow=which.min(output[,"measure"])
plot(output[,"measure"]~output[,"alpha"])
#best Alpha
output[bestRow,]
```




