---
title: "Homework III, due May 27th"
author: 
- M Loecher
- Yilun Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(titanic)
library (MASS)
library (ISLR)
```

#### This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.

#### 1. Review your understanding of **linear regression** using the book [An Introduction to Statistical Learning](http://faculty.marshall.usc.edu/gareth-james/ISL/)
  * Read chapters 3.1, 3.2.1, 3.3.1 
  * Reproduce Lab Exercises 3.6.4 (Interaction Terms) and 3.6.6 (Qualitative Predictors)
```{r}
# 3.6.4 Interaction Terms
summary (lm("medv~lstat*age" ,data=Boston ))

# 3.6.6 Qualitative Predictors
summary(lm(Sales ~ . +Income :Advertising +Price :Age ,data=Carseats ))
```


#### 2. Excercise 
Load the `titanic` library and the `titanic_train` data. In the following we use `Survived` as the outcome (y):
```{r echo = FALSE}
titanic_train$Pclass = as.factor(titanic_train$Pclass)
summary(lm("Survived~Pclass*Sex",data = titanic_train))
```

##### Fit a model containing the interactions between `Sex` and `Pclass`. Interpret the coefficients.
```{r echo = FALSE}
lm.fit=lm("Survived~Pclass:Sex",data = titanic_train)
summary(lm.fit)
```

###### Interpretation: 

   - The Interaction between male and class 2 seems to be insignificant to the prediction
   - Any predictions on whether the passenger survived is going to deviate by `r summary(lm.fit)$sigma` units (on average).
   - Overall, the model has an R-squared of `r summary(lm.fit)$r.sq`. This tells us that `r round(summary(lm.fit)$r.sq*100,2)`% of the variability in whether the person survived can be explained by this model. 

*** 
##### Fit a model containing the interactions between `Sex` and `age`. Interpret the coefficients.
```{r echo = FALSE}
lm.fit=lm("Survived~Sex:Age",data = titanic_train)
summary(lm.fit)
```

###### Interpretation:

   - Any predictions on whether the passenger survived is going to deviate by `r summary(lm.fit)$sigma` units (on average).
   - Overall, the model has an R-squared of `r summary(lm.fit)$r.sq`. This tells us that `r round(summary(lm.fit)$r.sq*100,2)`% of the variability in whether the person survived can be explained by this model. 

***

##### Fit a model containing the interactions between `Sex`, `Pclass` and `age`. Interpret the coefficients.
```{r echo = FALSE}
lm.fit=lm("Survived~Pclass:Sex:Age",data = titanic_train)
summary(lm.fit)
```
###### Interpretation:

   - Any predictions on whether the passenger survived is going to deviate by `r summary(lm.fit)$sigma` units (on average).
   - Overall, the model has an R-squared of `r summary(lm.fit)$r.sq`. This tells us that `r round(summary(lm.fit)$r.sq*100,2)`% of the variability in whether the person survived can be explained by this model. 
   