---
title: "Homework VII b, due July 1st"
author: "M Loecher"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rpart)
library(rpart.plot)
```

#### This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.

1. Learn about **classification and regression trees** using the book [An Introduction to Statistical Learning](https://westminster.instructure.com/courses/2915670/files/172215801) (formerly at http://faculty.marshall.usc.edu/gareth-james/ISL/)
   * Read chapter 8.1

2. Read the heart data set (https://web.stanford.edu/~hastie/ElemStatLearn//datasets/SAheart.info.txt) into R.
   * Fit a classification tree `chd ~ ., data=heart` using the `rpart` library  
   * The default plots are quite awful. For better plots use the library `rpart.plot`
   * Justify the very first split by computing the Gini index for **all possible splits of all possible variables**

```{r, eval = TRUE}
heart = read.table("http://www-stat.stanford.edu/~tibs/ElemStatLearn/datasets/SAheart.data", sep=",", head=T,row.names=1)
```

```{r}
heart.tree = rpart(chd ~.,data=heart)
rpart.plot(heart.tree)
```
```{r}
#function for calculating gini
gini.calc = function(x,var,col=x[,var],n=nrow(x),isBinary = length(unique(col)) == 2){
  if (isBinary){
    .class = unique(col)[1]
    n.obs = sum(col == .class)
    .p = n.obs/n
    return(.p*(1-.p))
  } else {
    .class = sort(unique(col))
    .gini = vapply(
      .class,
      function(X) {
        n.obs = sum(col<X)
        .p=n.obs/n
        return(.p*(1-.p))
      },
      numeric(1)
    )
    temp = cbind(.class,.gini)[-1,]
    colnames(temp) = c(paste(var,"<"),"Gini Index")
    max.gini=temp[which.max(temp[,2]),]
    min.gini=temp[which.min(temp[,2]),]
    result = rbind(max.gini,min.gini)
    result
  }
}
```


```{r}
gini.calc(heart,"sbp")
gini.calc(heart,"tobacco")
gini.calc(heart,"ldl")
gini.calc(heart,"adiposity")
gini.calc(heart,"typea")
gini.calc(heart,"obesity")
gini.calc(heart,"alcohol")
gini.calc(heart,"age")
gini.calc(heart,"famhist")
```




